\documentclass[11pt,margin,line]{cv}
\usepackage[colorlinks=true]{hyperref}
\usepackage{amssymb}
\usepackage{hyperref}
\hypersetup{urlcolor=black}


\newcommand{\sectionsp}{\vspace{-5mm}}
\setlength{\leftmargini}{0.15in}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Seunghyun Lee}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    2616 Erwin Rd, APT 2347                   \hfill mobile: 919 - 813 - 8382               \vspace{1mm}\\\vspace{0mm}%
    Durham, NC 27708          \hfill e-mail: \href{mailto:sl169@duke.edu}{sl169@duke.edu} \vspace{1mm}\\\vspace{-4.5mm}%
    %__________________________________________________________________________________________________________________
    % Research Interest
    \section{\mysidestyle Rearch\\Interests}
    Big Data Analytics, Data Intensive Computing, Machine Learning, Distributed Systems\vspace{1mm}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{Duke University}, Durham, NC \hfill \textbf{August 2009 -- present}\vspace{1mm}\\\vspace{0mm}%
    \textsl{Bachelor of Science in Computer Science, Minor in Mathematics}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Cumulative GPA: 3.75/4.0, Major GPA: 3.93/4.0
    \end{list3}
    \textbf{St.Anne's Belfield School}, Charlottesville, VA \hfill \textbf{August 2005 -- May 2009}\vspace{1mm}\\\vspace{0mm}%
    \textsl{High School Degree}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Graduated with Cum Laude, Unweighted GPA: 3.9/4.0
    \end{list3}

  %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Research\\Experience}
    \textbf{Connected Components on MapReduce}\hfill \textbf{May 2014 -- July 2014} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Advisor: Kamesh Munagala (Duke University)}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Implemented connected components algorthms and compared their performances.
        \item Implemented python scripts that converts the data into the visualization of the algorithm.
    \end{list3}
    \textbf{BigFrame}\hfill \textbf{August 2013 -- December 2013} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Advisor: Shivnath Babu (Duke University)}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
      \item Participated in a project that tries to build a benchmark generator for modern Big Data Analytics Systems.
      \item Set up and managed large clusters up to 100 nodes and conducted the performance tuning on Hadoop, Hive, and Spark.
      \item Ran performance tests under various conditions(scale-up, speed-up, scale-out) and conducted in-depth analysis.
    \end{list3}
    \textbf{Genomic Data Management Platform}\hfill \textbf{May 2013 -- June 2013} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Advisor: Shivnath Babu (Duke University)}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Testing the performance of Bioinformatics softwares such as Cloudburst, Cross-bow, and Myrna.
    \end{list3}

    %__________________________________________________________________________________________________________________
    % Work Experience
    \section{\mysidestyle Work\\Experience}
    \textbf{Frograms}, Seoul, Korea\hfill \textbf{September 2014 -- December 2014} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Software Engineer Intern}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Worked at a startup company that provides the service of movie recommendation.
        \item Designed and Implemented a quiz generating tool that is widely used in the businness team.
        \item Designed and Implemented a URL-shortener that provides a similar functionality to bitly.
    \end{list3}

    \textbf{SAP Labs}, Seoul, Korea\hfill \textbf{July 2013 -- August 2013} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Software Engineer Intern}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Conducted benchmarks of Hadoop, Spark, and SAP HANA and an in-depth analysis.
        \item Implemented python scripts for automating performance tests.
        \item Set up and managed the cluster with 160 cores, 2TB RAM.
    \end{list3}


    %__________________________________________________________________________________________________________________
    % Teaching Experience
    \section{\mysidestyle Teaching\\Experience}
    \textbf{Duke University}, Durham, NC\hfill \textbf{January 2013 -- May 2013} \vspace{1mm}\\\vspace{0mm}%
    \textsl{Undergraduate Teaching Assistant, Department of Computer Science}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Teaching Assistant for Data Strucures and Algorithms class, Instructor : Tabitha Peck.
        \item Conducted weekly office hours and graded programming assignments.
    \end{list3}

  %__________________________________________________________________________________________________________________
    % Course Projects
    \section{\mysidestyle Course\\Projects}
    \textbf{\textbf{OogaSalad}}\\
    \textsl{Duke University, CS308 - Software Design and Implementation}
    \begin{list3}
        \item Designed and implemented a turn-base strategy game engine in Java. Mostly worked on implementing the framework for serializing and deserializing game data in xml file format.
    \end{list3}
    \textbf{\textbf{SLogo}}\\
    \textsl{Duke University, CS308 - Software Design and Implementation}
    \begin{list3}
        \item Designed and implemented an interpreter of Logo Language in Java. Mostly worked on the back-end part that parses and build the execution tree of the user input commands.
    \end{list3}
    \textbf{\textbf{Devil Shell}}\\
    \textsl{Duke University, CS310 - Operating Systems}
    \begin{list3}
        \item Built a functional shell that supports spawning processes, job control, input/output redirection, error handling, and pipelines.
    \end{list3}
    \textbf{\textbf{Defiler}}\\
    \textsl{Duke University, CS310 - Operating Systems}
    \begin{list3}
        \item Implemented a multi-threaded file system in Java which is capable of storing and managing concurrent access to the multiple files.
    \end{list3}
  %__________________________________________________________________________________________________________________
    % Leadership Experience
    \section{\mysidestyle Leadership\\Experience}
    \textbf{Defense Security Command}, Kangwon Province, Korea \hfill \textbf{August 2010 -- May 2012}\vspace{1mm}\\\vspace{0mm}%
    \textsl{Seargent, Korean Army}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Served as a squad leader for 6 months and supervised 15 soldiers.
        \item Handled classified documents(Confidential-level 3, Secret-level 2).
    \end{list3}
    \textbf{Unrated}  \hfill \textbf{September 2009 -- present}\vspace{1mm}\\\vspace{0mm}%
    \textsl{Guitarist, Founding Member}
    \vspace{-2mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Organized weekly practice sessions and performances for various venues.
    \end{list3}
    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Awards}
    \begin{list3}
        \item Dean's List for Spring 2010, Fall 2012, Fall 2013, Spring 2014 (Duke University)
        \item Mathematics Award (St.Anne's Belfield School, 2009)
        \item The Hovey S. Dabney Scholarship (St.Anne's Belfield School, 2006)
    \end{list3}
    %__________________________________________________________________________________________________________________
    % Background
    \section{\mysidestyle Courses\\Taken}
    \begin{list3}
      \item Data Intensive Computing(Spring 2015), Network Architecture(Spring 2015), Operating Systems, Software Design \& Implementation, Data Structures, Design and Analysis of Algorithms, Computer Architecture, Computational Genomics
      \vspace{1mm}
      \item Coursera: Introduction to Databases(by Prof. Jennifer Wisdom, Stanford),  Introduction to Data Science(by Prof. Bill Howe, University of Washington)
    \end{list3}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Skills}
    \begin{list3}
        \item\textbf{Programming Languages:} Java, C, Python, Ruby, HTML/CSS/JS, SQL, \LaTeX
        \item\textbf{Software Tools:}  Hadoop/Hive, Spark, Ruby on Rails, Git
        \item\textbf{Operating Systems:} Linux, Mac OS, Windows
        \item\textbf{Languages:} Fluent in Korean and English; Basic Mandarin Chinese
    \end{list3}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}
