\documentclass[10pt,margin,line]{resume}
\usepackage[colorlinks=true]{hyperref}
\usepackage{amssymb}
\usepackage{hyperref}
\hypersetup{urlcolor=black}


\newcommand{\sectionsp}{\vspace{-5mm}}
\setlength{\leftmargini}{0.15in}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Seunghyun Lee}
\begin{resume}

%__________________________________________________________________________________________________________________
% Contact Information
\section{\mysidestyle Contact\\Information}
mobile: 412 - 737 - 0925          		\vspace{0mm}\\\vspace{0mm}%
e-mail: \href{mailto:seunghy1@andrew.cmu.edu}{seunghy1@andrew.cmu.edu}	\vspace{0mm}\\\vspace{-4.5mm}%

%__________________________________________________________________________________________________________________
% Education
\section{\mysidestyle Education}
\textbf{Carnegie Mellon University, School of Computer Science}, Pittsburgh, PA \\\vspace{0mm}%
\textsl{Master of Computational Data Science, Systems Major} \hfill \textbf{December 2016 (Expected)}
\vspace{-3mm}\\\vspace{-1mm}%
\begin{list3}
    \item GPA: 3.58/4.0
    \item Course Highlights: Distributed Systems, Cloud Computing, Database Systems, Multimedia Databases and Data Mining, Machine Learning, Introduction to Computer Systems
\end{list3}

\textbf{Duke University}, Durham, NC \vspace{0mm}\\\vspace{0mm}%
\textsl{Bachelor of Science in Computer Science, Minor in Mathematics}\hfill \textbf{May 2015}
\vspace{-3mm}\\\vspace{-1mm}%
\begin{list3}
    \item GPA: 3.68/4.0
    \item Awards: Dean's List for Spring 2010, Fall 2012, Fall 2013, Spring 2014
    \item Course Highlights: Data-Intensive Computing Systems, Computer Networks, Operating Systems, Software Design \& Implementation, Data Structures, Algorithms, Computer Architecture
\end{list3}

%__________________________________________________________________________________________________________________
% Work Experience
\section{\mysidestyle Work\\Experience}

\textbf{LinkedIn}, Mountain View, CA\hfill \textbf{May -- August 2016} \vspace{0mm}\\\vspace{0mm}%
\textsl{Software Engineering Intern, Data Infrastructure}
\vspace{-3mm}\\\vspace{-1mm}%
\begin{list3}
    \item Developed a deep understanding of data models for streaming engines such as Dataflow and DStream.
    \item Designed and implemented a proof of concept streaming data pipeline that computes business metrics using Apache Beam SDK.
\end{list3}


\textbf{SAP Labs Korea}, Seoul, Korea\hfill \textbf{July -- August 2013} \vspace{0mm}\\\vspace{0mm}%
\textsl{Software Engineering Intern}
\vspace{-3mm}\\\vspace{-1mm}%
\begin{list3}
    \item Conducted a rigorous performance comparisons on Hadoop/Hive, Spark/Shark, and SAP HANA using TPC-H data set and its queries.
    \item Deployed and managed a large cluster with two hundred cores and 2TB RAM.
\end{list3}

\textbf{Watcha}, Seoul, Korea\hfill \textbf{September -- December 2014} \vspace{0mm}\\\vspace{0mm}%
\textsl{Software Engineering Intern}
\vspace{-3mm}\\\vspace{-1mm}%
\begin{list3}
    \item Designed and implemented a quiz and poll generating tool using Ruby on Rails and MySQL.
    \item Designed and implemented a backend part of an analytics tool that visualizes the business metrics.
\end{list3}

%__________________________________________________________________________________________________________________
% Research Projects
\section{\mysidestyle Projects}
\textbf{Intelligent Scheduling on YARN}\hfill \textbf{March -- May 2016} \vspace{0mm}\\\vspace{0mm}%
\vspace{-7mm}\\\vspace{-1mm}%
\begin{list3}
    \item Designed and implemented the heterogeneity-aware resource scheduler that communicates through YARN's resource manager with RPC interface using Apache Thrift.
    \item Implemented various resource scheduling algorithms including FIFO, shortest job first, and highest utility first.
\end{list3}

\textbf{User Defined Function on Peloton}\hfill \textbf{March -- May 2016} \vspace{0mm}\\\vspace{0mm}%
\vspace{-7mm}\\\vspace{-1mm}%
\begin{list3}
    \item Added the UDF functionality by extending the expression system of Peloton, which is an in-memory database system that is developed at CMU.
    \item Performed the benchmark and compared the performance between stored procedures and prepared statements.
\end{list3}

\textbf{Twitter Analytics Web Service}\hfill \textbf{October -- December 2015} \vspace{0mm}\\\vspace{0mm}\vspace{-7mm}\\\vspace{-1mm}%
\begin{list3}
    \item Performed ETL over a large tweet dataset (over 1TB) using Hadoop EMR.
    \item Improved the performance of MySQL and HBase by using index and optimizing the schema.
    \item Scaled out our systems using Elastic Load Balancer from AWS.
\end{list3}

\textbf{GraphMiner}\hfill \textbf{March -- May 2016} \vspace{0mm}\\\vspace{0mm}%
\vspace{-7mm}\\\vspace{-1mm}%
\begin{list3}
    \item Implemented a k-core degeneracy algorithm with SQL and analyzed the effect of different indexing methods (B-tree, clustered) and data re-ordering.
    \item Observed the results of data mining algorithms such as degree distribution, page rank, k-coreness, and connected components and performed in-depth analysis on 10 different graph data.
\end{list3}


% \textbf{YARN Resource Management and Scheduling}\hfill \textbf{March 2015 -- May 2015} \vspace{0mm}\\\vspace{0mm}%
% \vspace{-7mm}\\\vspace{-1mm}%
% \begin{list3}
%     \item Implemented the framework for profiling scheduler's metrics information using YARN's REST API.
%     \item Set up two different scenarios (batch and interactive intensive) using MapReduce/Hive, and conducted experiments to optimize configurations for Capacity Scheduler.
%     \item Improved the performance of the base case by 20\%.
% \end{list3}

% \textbf{Connected Components on MapReduce}\hfill \textbf{May 2014 -- July 2014} \vspace{0mm}\\\vspace{0mm}%
% \vspace{-7mm}\\\vspace{-1mm}%
% \begin{list3}
%     \item Implemented existing MapReduce algorithms for connected components such as Hash-Min, Hash-To-All, Hash-To-Min on top of Spark.
%     \item Conducted in-depth comparisons of algorithms by analyzing collected data such as the execution time, the number of iterations, and the size of intermediate data.
% \end{list3}




%__________________________________________________________________________________________________________________
% Computer Skills
\section{\mysidestyle Skills}
    Java, Python, C/C++, Hadoop, Spark, SQL, HTML/CSS/JS, Ruby on Rails, Git, Amazon AWS\\

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}
